An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2010-12-19 paper.tex
Added references in Section 5.

Gravitational-wave astronomy provides the setting for another ongoing
study.  Interesting triggers from the LIGO and Virgo
gravitational-wave detector pipeline that searches for compact binary
coalescences are followed up with Bayesian parameter estimation tools.
In general, several possible models for the data are considered,
including a pure noise model, noise superimposed on a non-spinning
gravitational-wave signal, or noise superimposed on a gravitational
wave signal that includes significant spin or spins in the binary
components.  The models can include a large number of parameters (up
to 15 for the model with two spinning components), and RJMCMC with
interpolation via kD trees is again successful at computing the model
evidences. \ilya{Add references throughout this paragraph.}

>>>>

Gravitational-wave astronomy provides the setting for another ongoing
study.  Interesting triggers from the LIGO \cite{InitLIGO} and Virgo \cite{Virgo}
gravitational-wave detector pipeline that searches for compact binary
coalescences are followed up with Bayesian parameter estimation tools (see, e.g., \cite{Rover:2006ni, vanderSluys:2008b, VeitchVecchio:2009}).
In general, several possible models for the data are considered,
including a pure noise model, noise superimposed on a non-spinning
gravitational-wave signal, or noise superimposed on a gravitational
wave signal that includes significant spin or spins in the binary
components.  The models can include a large number of parameters (up
to 15 for the model with two spinning components \cite{Raymond:2010}), and RJMCMC with
interpolation via kD trees is again successful at computing the model
evidences.
